\chapter{Introduction}

%\chapter*{Introduction}
\label{intro}

It is worth mentioning that this work was initially started out of the author's desire to become more intimate with the concepts of AI. From the perspective of a novice, there was little to no hope of achieving a barely functional result, and the thought of crafting a breakthrough solution in the field was not realistically possible due to fragile knowledge and lack of expertness. In the virtue of honesty, it is to be said that this work is trading high expectations for invaluable experience. The reader is invited to a an itinerary seen from the eyes of someone who is carefully discovering and observing the world full of wonders of artificial intelligence. 

The case study chosen to perform experiments on is handwriting recognition, the process through which a computer is trying to mimick the human natural ability to read text from visual sources. Chapter \ref{chap:ch2} contains more technical details about the problem. In chapter \ref{chap:ch3}, a handful of theoretical concepts regarding machine learning have been compiled into a friendly form, starting with the mathematical foundations and culminating with neural network layers and architectures. Chapter \ref{chap:ch4} describes how these neural networks are used in literature to build a solution to the handwritten text recognition problem. The author's own attempt to perform text line segmentation and train a recognition model on English-Romanian handwritten text samples is all wrapped up in chapter \ref{chap:ch5}. Finally, chapter \ref{chap:ch6} describes the architecture of a simple intelligent system running on Android devices entirely client side that tries to use the previously described solution in predicting text from camera captured images and store the result on the filesystem's memory. For the purpose of learning, the model inference has been coded from scratch, without any help from AI libraries. 