%\documentclass[12pt]{scrreprt}
\documentclass[12pt]{report} 

\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}

% language may be romanian or english (default is english)
% type may be bachelor or master (default is bachelor)
\usepackage[language=english, type=bachelor]{style}

%\geometry{a4paper,top=2.5cm,left=3cm,right=2.5cm,bottom=2.5cm}
%in style
%controlling the appearance of your headers and footers
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{color}
\pagestyle{fancy}
\usepackage{floatrow}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{listings}
\usepackage{caption}
\lhead{}
\chead{}
\renewcommand{\headrulewidth}{0.2pt}
\renewcommand{\footrulewidth}{0.2pt}

\begin{document}

\specialization{Computer Science}	
\title{Handwritten text recognition techniques applied on English-Romanian texts}
\author{Neac\c{s}u-Miclea Liviu-\c{S}tefan}
\supervisor{Prof. Laura Dio\c{s}an}		

\maketitle


\newpage
\thispagestyle{empty}
\mbox{}
\newpage
\pagenumbering{roman} 

\cleardoublepage
ABSTRACT
\vspace{0.5cm}	
\hrule
\vspace{0.5cm}	
%\cleardoublepage

This work is an attempt to address the handwritten text recognition (HTR) problem using a deep learning approach. The solution recipe involves three steps: text line segmentation performed by a fused U-Net-LSTM model, line extraction and reconstruction postprocessing, and line level text recognition via a CRNN model.

The thesis seven chapters are structured in a progressive manner. The introduction describes the motivation of this project. Next, there is a short summary about OCR, followed by a chapter providing an insightful picture behind the scenes of neural networks and a literature survey. Then, a new image text line extraction algorithm is presented as well as a particularization of a CNN-LSTM-CTC based line recognition model on the Romanian language, along with experimental details and results. The entire system has been showcased into a simple mobile application capable of taking pictures of documents and predicting whatever is written in there. The technical matters are covered in a separate chapter. Finally, some thoughts are expressed on possible refinement and further development of the presented approach.

\tableofcontents
% \listoffigures

\newpage
\pagenumbering{arabic}


\input{chapters/chapter1_introduction}
%\addcontentsline{toc}{chapter}{Introducere}
%\addcontentsline{toc}{chapter}{Introduction}

\input{chapters/chapter_2_OCR}
\input{chapters/chapter_3_NeuralNetworks}
\input{chapters/chapter_4_HTR}
\input{chapters/chapter_5_Proposed_Approach}
\input{chapters/chapter_6_App}
\input{chapters/chapter_7_conclusion}


\bibliography{references}

\end{document}
